Thesis plan\\Version 1.0

### 2018-04-09 Thesis plan/Thesis plan.tex
Updated research question and hypothesis

\item{What is the relationship between the accuracy of an embedding method and the type of text?}

@@

\section{Research method}
\subsection{Method \& Validation}
\paragraph{Method} To answer the stated research questions, a fitted approach must be applied. For this project, the research method '\textit{Controlled Experiments}' will be applied. Using this methodology, the goal of this project is to validate these two hypothesis:
\begin{itemize}
\item{The word-to-vec embedding method can have an higher accuracy for academic texts than the TF-IDF algorithm.}
\item{The accuracy of academic embedding methods can be validated using categorization tasks}
\end{itemize}
\paragraph{Validation} This research will be validated via a clear presentation of all compared results. The usage of a publicly available collection and via a clear presentation of the used parameters for each method.

>>>>

\item{Which metric(s) can be used to measure the accuracy of word embeddings for scientific articles?}

@@

\section{Research method}
\subsection{Method \& Validation}
\paragraph{Method} To answer the stated research questions, a fitted approach must be applied. For this project, the research method '\textit{Controlled Experiments}' will be applied. Using this methodology, the goal of this project is to validate these two hypothesis:
\begin{itemize}
\item{The word-to-vec embedding method can have an higher accuracy for academic texts than the TF-IDF algorithm.}
\item{The accuracy of academic embedding methods can be validated using classification tasks}
\end{itemize}
\paragraph{Validation} This research will be validated via a clear presentation of all compared results. The usage of a publicly available collection and via a clear presentation of the used parameters for each method.
